---
title: "titanic survivors part 1"
author: "beniamino di maro"
date: "2/28/2018"
output: html_document
---

## From the work of Hitesh Palamada "Head Start for Data Scientist"

In this first attempt I'll take all information given by the author to better understand how to make a good analysis
of a data set on titanic survivors

# Installing all necessary libraries

```{r, message = FALSE}
# data wrangling
library(tidyverse)
library(forcats)
library(stringr)
library(caTools)

# data assessment/visualizations
library(DT)
library(data.table)
library(pander)
library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
library(corrplot)
library(VIM) 
library(knitr)
library(vcd)
library(caret)


# model
library(xgboost)
library(MLmetrics)
library('randomForest') 
library('rpart')
library('rpart.plot')
library('car')
library('e1071')
library(vcd)
library(ROCR)
library(pROC)
library(VIM)
library(glmnet) 
```

# Load the dataset

```{r}
train <- read.csv('train.csv')
test  <- read.csv('test.csv')
```

For studing the complete data set lets join test and train data set.
Before that we will add a new coloum “set” and give name as ‘test’ for test dataset
and ‘train’ for train dataset to have an idea about which record it is.

```{r}
train$set <- "train"
test$set  <- "test"
test$Survived <- NA
full <- rbind(train, test)
```
